%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Alexander Chepurnoy Resume/CV
% LaTeX Template
% Version 1.1 (20/7/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Cies Breijs (cies@kde.nl)
% https://github.com/cies/resume with extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,a4paper]{article} % Font size (10-12pt) and paper size (a4paper, letterpaper, legalpaper, etc)

\include{structure} % Include structure.tex which contains packages and document layout definitions

\hyphenation{Some-long-word} % Specify custom hyphenation points in words with dashes where you would like hyphenation to occur, or alternatively, don't put any dashes in a word to stop hyphenation altogether

\begin{document} 

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\maintitle{Alexander Chepurnoy}{7$^{th}$ February 1984}  % Your name and date of birth or subtitle

\noindent\href{mailto:kushti@protonmail.ch}{kushti@protonmail.ch}\bull % Your email address
\textit{(Skype: sandylabs)}\bull % Your phone number(s) and Skype username
\href{http://chepurnoy.org}{chepurnoy.org}\\ % Your URL
Sestroretsk\bull Russia % Your address

\spacedhrule{0.9em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\roottitle{Summary} % Root section title

\vspace{-1.3em} % Reduce whitespace after the Summary heading and the two-column content

\begin{multicols}{2}  % Start a two-column layout
\noindent \textit{A summary}\\\\
I am an experienced and passionated engineer and researcher. I have built many products while enjoying design, development and management processes. I tried many programming languages using current favourite one, Scala, since 2011. I love functional programming, programming languages theory and CS knowledge in general. 

Previously I worked on data harvesting and analysis tools. Now I am living in the blockchain world and willing to continue to be here for coming years.  Also I love to have results of my work as open as possible to wider public. 

\end{multicols}

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\roottitle{Experience} % Top level section

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://iohk.io/}{IOHK Research}}
{

\headedsubsection % Job title entry for the current employer
{\acr{Project Scorex Director}/\acr{Researcher}}
{Feb 2015 -- now}
{\bodytext{Developing Scorex and doing a research on blockchains.}}
}

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://smartcontract.com/}{Smart Contract}}
{

\headedsubsection % Job title entry for the current employer
{\acr{CoFounder}/\acr{Backend Developer}}
{Oct 2014 -- Dec 2015}
{\bodytext{SmartContract is building escrow schemes automatically executed based on public datafeeds. Contracts and their updates are being written into Nxt blockchain in clear-text or hashed form. Previously the team built Secure Assets Exchange, web layer on top of decentralized Nxt Assets Exchange with some additional functionality. I designed and developen backend with Scala, Akka, Spray for both products, releasing \href{https://github.com/kushti/NxtScala}{NxtScala} open-source micro-framework on the way.}}
}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://nxt.org}{Nxt cryptocurrency}}
{

\headedsubsection % Job title entry for the current employer
{\acr{Core Developer}}
{Apr 2014 -- Apr 2015}
{\bodytext{Nxt is a cryptocurrency built from scratch, delivering decentralized economy platform. I developed first integration tests, alias transfer, voting system, 2-phased transactions(multisig for Nxt). Also I made some amount of documentation and specifications, key users support. }}

\headedsubsection % Job title entry for the current employer
{\acr{Consensus Research}}
{Nov 2014 -- Feb 2015}
{\bodytext{Consensus Research is informal research micro-group made research on Nxt-like Proof-of-Stake algorithm properties by gathering statistics from simulations made with Haskell and Coq. All known attacks were modelled along with papers published online.}}

}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{NovaShelf} {

\headedsubsection % Job title entry for the current employer
{Freelance Software Engineer}
{Sep 2013 -- Apr 2014}
{\bodytext{Stealth mode startup developed a new approach to clusterize documents based on Kohonen Self-Organized Maps. I built a distributed and decentralized system for crawling/processing/semantic clusterization of documents using Scala, Akka, Riak, OpenNLP, Lucene.}}
}

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{https://en.wikipedia.org/wiki/Domain_Developers_Fund}{Domain Developers Fund}} {

\headedsubsection % Job title entry for the current employer
{Freelance Software Engineer}
{Jun 2013 -- Dec 2013}
{\bodytext{Domain Developers Fund is the first public open-ended alternative investment fund exclusively invested in Internet domain names. It built a number of data collection and analysis tools using Scala, Java, Akka, MongoDB, Apache HttpClient, HtmlUnit, PlayFramework.}}
}

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{HedgeWallet} {

\headedsubsection % Job title entry for the current employer
{Freelance Software Engineer}
{Mar 2013 -- Nov 2013}
{\bodytext{Stealth mode startup to hold bitcoins and fiat currencies with auto hedging. I built user web application backend using Groovy, Grails, ProstgreSQL}}
}

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{RankRust} {

\headedsubsection % Job title entry for the current employer
{Software Engineer, Tech Lead}
{Feb 2011 -- Feb 2013}
{\bodytext{Private company in Czech Republic made SEO tools and SEO-related data harvesting. I built a crawling system using Java, Nutch, Solr, PostgreSQL, RabbitMQ}}
}


%------------------------------------------------

\headedsection
{DelightCash} {

\headedsubsection 
{\acr{Tech Lead, CTO}}
{May 2009 -- Feb 2011}
{\bodytext{Adult affiliate program. I managed all the technical processes around it.}}
}

%------------------------------------------------

\headedsection
{Exigen Services} {

\headedsubsection 
{\acr{Software Engineer}}
{Jun 2006 -- Nov 2007}
{\bodytext{Those days Exigen Services was the biggest software development outsourcing company in Eastern Europe and CIS countries. The main project I worked on is professional all-in-one database security and auditing solution for Oracle, Sybase, DB2, MySQL and Microsoft SQL Server used by 3M, IBM, JP Morgan Chase, Hewlett- Packard, Shell, Sony and many others. Java, Struts, SQL code specific to most popular relational databases(MySQL, Oracle, MS SQL Server, Sybase, IBM DB2). }}
}

\begin{flushleft}
\textit{Please refer my \href{https://github.com/kushti}{GitHub account} for contributions to open source made by me(Scala mostly). Also please refer to \href{https://www.upwork.com/freelancers/~01de607007b5965edf}{my ODesk profile} for more jobs done along with recommendations.}
\end{flushleft}

%------------------------------------------------

\spacedhrule{-0.2em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------


\roottitle{Education} % Top level section

\headedsection
{Information Technologies, Mechanics and Optics (ITMO) University}
{\textsc{Saint-Petersburg, Russia}} {

\headedsubsection 
{\acr{Diploma of Specialist in Computer Systems}}
{2001 -- 2007}
{\bodytext{CS education providing both hardware and software knowledge with focus on embedded software development. A thesis was supervised by \href{https://scholar.google.ru/scholar?q=Ojiganov&btnG=&hl=en}{professor Ojiganov} and named like ``An Automated System for Recursive Code Scales Calculation''.}}
}



I also have unfinished PHD with few papers published in peer-reviewed journals(in Russian only to the moment) in the area of reactive software modelling with finite state machines. 

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\roottitle{Skills} % Top level section

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Technical specialties:}
{Languages: Scala, Java, Groovy. In past I used C, C++, PHP to earn money. Playing with Haskell, Coq, OCaml, Idris. Many other languages were used (from Pascal to NuSMV) but now forgotten. Databases: PostgreSQL, Riak, MongoDB, Hazelcast, FoundationDB. Frameworks: Akka, Spray, Slick, MapDb.   
Miscellanous: git, LaTEX, Markdown.}

%------------------------------------------------

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Natural languages:}
{Russian \textit{(mother tongue)}, English \textit{(full professional proficiency)}}

%------------------------------------------------

\spacedhrule{1.6em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

\end{document}